FEM Model Analysis

### 2021-01-12 FEM_R/model_analysis.Rmd
WIP few chunks in model_analysis.Rmd for comparing simulation to AgeUK almanac

```{r}
# Need a function here to handle the repetition
get_prevalence <- function(FEM) {

}

@@

# Now get FEM output for 2014
FEM_2014 <- read_dta('ELSA_Baseline/detailed_output/y2014_rep1.dta')
FEM_2014 <- FEM_2014[keep_vars]
# extract males and females
mFEM_2014 <- FEM_2014 %>% filter(male == 1)
fFEM_2014 <- FEM_2014 %>% filter(male == 0)

@@

# correct colnames in ageUK stuff
male_ageUK <- male_ageUK %>% filter(conditions == c('Hypertension', 'Stroke', 'Diabetes', 'Dementia'))

# Now calculate prevalence by age group for each chronic disease
# prevalence = total / affected
# Diabetes
male_prev <- data.frame(colSums(mFEM_2014) / nrow(mFEM_2014))
female_prev <- data.frame(colSums(fFEM_2014) / nrow(fFEM_2014))
colnames(male_prev) <- 'FEM_male'
colnames(female_prev) <- 'FEM_female'

>>>>

```{r}
# Need a function here to handle the repetition
get_FEM_prev <- function(FEM, age_range, keep_vars) {
  # Keep only important vars
  FEM <- FEM[keep_vars]
  # Separate by gender
  mFEM <- FEM %>% filter(male == 1)
  fFEM <- FEM %>% filter(male == 0)
  # Filter by age from age_range
  mFEM <- mFEM %>% filter(age %in% (age_range))
  fFEM <- fFEM %>% filter(age %in% (age_range))
  # Get proportion of total pop. (prevalence)
  mFEM <- data.frame((colSums(mFEM) / nrow(mFEM)) * 100)
  fFEM <- data.frame((colSums(fFEM) / nrow(fFEM)) * 100)

  # produce a string for column naming
  age <- paste0(age_range[1], '-', age_range[5])

  colnames(mFEM) <- paste0('FEM_male_', age)
  colnames(fFEM) <- paste0('FEM_female_', age)

  #male <- cbind(male, mFEM)

  # Collect into 1 df
  prev_df <- data.frame(mFEM, fFEM)
  return(prev_df)

  #return(out)
}

package <- function() {
  # Set up objects for holding and returning the prevalences, separate dfs for male and female
  out <- list()
  male <- data.frame()
  female <- data.frame()

  age_list <- c('Age 60-64', 'Age 65-69', 'Age 70-74', 'Age 75-79', 'Age 80-84', 'Age 85-89', 'Age 90-94', 'Age 95-99', 'Age 100+')
  age_list <- c(60:64, 65:69, 70:74, 75:79, 80:84, 85:89, 90:94, 95:99)
}

@@

# Now get FEM output for 2014
FEM_2014 <- read_dta('ELSA_Baseline/detailed_output/y2014_rep1.dta')

test <- get_FEM_prev(FEM_2014, 60:64, keep_vars)

#FEM_2014 <- FEM_2014[keep_vars]
## extract males and females
mFEM_2014 <- FEM_2014 %>% filter(male == 1)
fFEM_2014 <- FEM_2014 %>% filter(male == 0)

@@

# AgeUK conditions to extract
#condlist <- c('Dementia', 'Hypertension', 'Diabetes', 'Stroke')

# correct colnames in ageUK stuff
#male_ageUK <- male_ageUK %>% filter(Condition == 'Dementia' | Condition == 'Hypertension' | Condition == 'Diabetes' | Condition == 'Stroke')
#male_ageUK <- male_ageUK %>% filter(Condition %in% condlist)

# Now calculate prevalence by age group for each chronic disease
# prevalence = total / affected
# Diabetes
#male_prev <- data.frame(colSums(mFEM_2014) / nrow(mFEM_2014))
#female_prev <- data.frame(colSums(fFEM_2014) / nrow(fFEM_2014))
#colnames(male_prev) <- 'FEM_male'
#colnames(female_prev) <- 'FEM_female'

tmp <- function(m, f, age) {

  m_age <- m %>% filter(age %in% (age))
  f_age <- f %>% filter(age %in% (age))

  m_prev <- data.frame((colSums(m_age) / nrow(m_age)) * 100)
  f_prev <- data.frame((colSums(f_age) / nrow(f_age)) * 100)

  list <- list(m_prev, f_prev)
  return(list)
}

# Now get FEM output for 2014
FEM_2014 <- read_dta('ELSA_Baseline/detailed_output/y2014_rep1.dta')
FEM <- FEM_2014[keep_vars]

# extract males and females
mFEM <- FEM %>% filter(male == 1)
fFEM <- FEM %>% filter(male == 0)

age_list <- c(60:64, 65:69, 70:74, 75:79, 80:84, 85:89, 90:94, 95:99)

m6064 <- mFEM %>% filter(age %in% (60:64))
f6064 <- fFEM %>% filter(age %in% (60:64))

male <- list()
female <- list()

mf_list <- tmp(mFEM, fFEM, 60:64)
male <- list(male, mf_list[1])
female <- list(female, mf_list[2])
